Analysis of Tick-Bourne Disease Cases Reported to DPH Between 2019-2024

### 2025-04-26 products/manuscript/Manuscript.qmd

+-----------+-----------+-----------+-----------+-----------+
| term      | estimate  | s         | statistic | p.value   |
|           |           | td.error  |           |           |
| \<chr\>   | \<dbl\>   |           | \<dbl\>   | \<dbl\>   |
|           |           | \<dbl\>   |           |           |
+:==========+==========:+==========:+==========:+==========:+
| (         | -2 3 2    | 1 57      | 1         | 0.1729390 |
| I         | 8.5151515 | 3.052665  | .48025251 |           |
| ntercept) |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| YEAR      | 1.1515152 | 0.777581  | 1         | 0.1727716 |
|           |           |           | .48089418 |           |
+-----------+-----------+-----------+-----------+-----------+
| B         | 0.4242424 | 5.484565  | 0         | 0.9400358 |
| ABESIOSIS |           |           | .07735207 |           |
+-----------+-----------+-----------+-----------+-----------+
| DENGUE    | 4.8484848 | 6.364775  | 0         | 0.4656907 |
|           |           |           | .76176850 |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | 5.0000000 | 5.157889  | 0         | 0.3576794 |
| C         |           |           | .96938889 |           |
| H         |           |           |           |           |
| AFFEENSIS |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | -         | 6.364775  | 0         | 0.8604390 |
| EWINGII   | 1.1515152 |           | .18092002 |           |
+-----------+-----------+-----------+-----------+-----------+
| LYME      | 8.5606061 | 4.963745  | 1         | 0.1186814 |
| DISEASE   |           |           | .72462659 |           |
+-----------+-----------+-----------+-----------+-----------+
| ROCKY     | 0.5757576 | 5.484565  | 0         | 0.9186958 |
| MOUNTAIN  |           |           | .10497781 |           |
| SPOTTED   |           |           |           |           |
| FEVER     |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| WEST NILE | 8.2272727 | 5.593721  | 1         | 0.1754208 |
| (WNV)     |           |           | .47080497 |           |
| INFECTION |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+

@@

+--------+--------+--------+--------+--------+
| term   | e      | s t    | s t    | p      |
|        | s      | d      | a      | .value |
| \      | timate | .error | tistic |        |
| <chr\> |        |        |        | \      |
|        | \      | \      | \      | <dbl\> |
|        | <dbl\> | <dbl\> | <dbl\> |        |
+:=======+=======:+=======:+=======:+=======:+
| ( I n  | 9 9 3  | 5 7 2  | 1      | 0 .    |
| t      | 5      | 9      | .      | 1      |
| e      | .      | .      | 733920 | 434648 |
| rcept) | 267857 | 946482 |        |        |
+--------+--------+--------+--------+--------+
| YEAR   | -   4  | 2      | -   1  | 0 .    |
|        |     .  | .      |     .  | 1      |
|        | 910714 | 835202 | 732051 | 438108 |
+--------+--------+--------+--------+--------+

>>>>

+-----------+-----------+-----------+-----------+-----------+
| term      | estimate  | s         | statistic | p.value   |
|           |           | td.error  |           |           |
| \<chr\>   | \<dbl\>   |           | \<dbl\>   | \<dbl\>   |
|           |           | \<dbl\>   |           |           |
+:==========+==========:+==========:+==========:+==========:+
| ( I       | -2 3 2    | 1 57      | 1         | 0.1729390 |
| ntercept) | 8.5151515 | 3.052665  | .48025251 |           |
+-----------+-----------+-----------+-----------+-----------+
| YEAR      | 1.1515152 | 0.777581  | 1         | 0.1727716 |
|           |           |           | .48089418 |           |
+-----------+-----------+-----------+-----------+-----------+
| B         | 0.4242424 | 5.484565  | 0         | 0.9400358 |
| ABESIOSIS |           |           | .07735207 |           |
+-----------+-----------+-----------+-----------+-----------+
| DENGUE    | 4.8484848 | 6.364775  | 0         | 0.4656907 |
|           |           |           | .76176850 |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | 5.0000000 | 5.157889  | 0         | 0.3576794 |
| C H       |           |           | .96938889 |           |
| AFFEENSIS |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | -         | 6.364775  | 0         | 0.8604390 |
| EWINGII   | 1.1515152 |           | .18092002 |           |
+-----------+-----------+-----------+-----------+-----------+
| LYME      | 8.5606061 | 4.963745  | 1         | 0.1186814 |
| DISEASE   |           |           | .72462659 |           |
+-----------+-----------+-----------+-----------+-----------+
| ROCKY     | 0.5757576 | 5.484565  | 0         | 0.9186958 |
| MOUNTAIN  |           |           | .10497781 |           |
| SPOTTED   |           |           |           |           |
| FEVER     |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| WEST NILE | 8.2272727 | 5.593721  | 1         | 0.1754208 |
| (WNV)     |           |           | .47080497 |           |
| INFECTION |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+

@@

+--------+--------+--------+--------+--------+
| term   | e s    | s t d  | s t a  | p      |
|        | timate | .error | tistic | .value |
| \      |        |        |        |        |
| \      | \      | \      | \      | \      |
| <chr\> | \      | \      | \      | \      |
|        | <dbl\> | <dbl\> | <dbl\> | <dbl\> |
+:=======+=======:+=======:+=======:+=======:+
| ( I n  | 9 9 3  | 5 7 2  | 1 .    | 0 . 1  |
| t e    | 5 .    | 9 .    | 733920 | 434648 |
| rcept) | 267857 | 946482 |        |        |
+--------+--------+--------+--------+--------+
| YEAR   | -   4  | 2 .    | -   1  | 0 . 1  |
|        |     .  | 835202 |     .  | 438108 |
|        |        |        |        |        |
|        | 910714 |        | 732051 |        |
+--------+--------+--------+--------+--------+
